---
title: "Portfolio_1"
author: "Lindley Slipetz"
date: "2/12/2021"
output: html_document
---

In this portfolio piece, we will look at how people's relationship to cooking and baking has changed pre- and during Covid. There are four spreadsheets in this file. I'm leaving off the first sheet because it uses a different scale than the other sheets. Also, there is no documentation for this data, and it's not exactly clear how the first sheet is measuring google trends. The final three are number of mentions of the activities on Twitter, Forums, and Blogs. Let's load some data! 

```{r setup, warning = FALSE}
library(readxl)
Cooking_Twitter_raw <- read_excel("G:/My Drive/DataScience/Covid/Cooking.xlsx", sheet = 2)
Cooking_Forums_raw <- read_excel("G:/My Drive/DataScience/Covid/Cooking.xlsx", sheet = 3)
Cooking_Blogs_raw <- read_excel("G:/My Drive/DataScience/Covid/Cooking.xlsx", sheet = 4)
```

This data is messy. Let's make it tidy! I'm not going to even try to work within these dataframes because they're just that messy. Let's start by making a new dataframe! We'll just get the columns together first and then we'll add the data.

```{r columns}
cooking_columns <- c("Venue", "Timepoint", "Recipes", "Baking_Bread", "Sourdough", "Cooking_directions", "Cook")
cooking_data <- as.data.frame(matrix(ncol = length(cooking_columns), nrow=0, dimnames = list(NULL,cooking_columns)) )
```

Okay, time to add the data to the new dataframe. 
df$major[df$degree1 == "BA"]
```{r add_data}
##Blog time 1
cooking_data <-rbind(cooking_data, data.frame(
   Venue = "Blog",
   Timepoint = 1,
   Recipes = Cooking_Blogs_raw$`Mentions before March 13 (January 3, 2020-March 12, 2020)...8`[Cooking_Blogs_raw$...7 == "Recipes" & is.na(Cooking_Blogs_raw$...7) == FALSE],
   Baking_Bread = Cooking_Blogs_raw$`Mentions before March 13 (January 3, 2020-March 12, 2020)...8`[Cooking_Blogs_raw$...7 == "Baking bread" & is.na(Cooking_Blogs_raw$...7) == FALSE], 
   Sourdough = Cooking_Blogs_raw$`Mentions before March 13 (January 3, 2020-March 12, 2020)...8`[Cooking_Blogs_raw$...7 == "Sourdough" & is.na(Cooking_Blogs_raw$...7) == FALSE],
   Cooking_directions = Cooking_Blogs_raw$`Mentions before March 13 (January 3, 2020-March 12, 2020)...8`[Cooking_Blogs_raw$...7 == "Cooking Directions" & is.na(Cooking_Blogs_raw$...7) == FALSE],
   Cook = Cooking_Blogs_raw$`Mentions before March 13 (January 3, 2020-March 12, 2020)...8`[Cooking_Blogs_raw$...7 == "Cook" & is.na(Cooking_Blogs_raw$...7) == FALSE]))
##Blog time 2  
cooking_data <-rbind(cooking_data, data.frame(
   Venue = "Blog",
   Timepoint = 2,
   Recipes = Cooking_Blogs_raw$`Mentions after March 13 (March 14, 2020-May 22, 2020)...10`[Cooking_Blogs_raw$...7 == "Recipes" & is.na(Cooking_Blogs_raw$...7) == FALSE],
   Baking_Bread = Cooking_Blogs_raw$`Mentions after March 13 (March 14, 2020-May 22, 2020)...10`[Cooking_Blogs_raw$...7 == "Baking bread" & is.na(Cooking_Blogs_raw$...7) == FALSE], 
   Sourdough = Cooking_Blogs_raw$`Mentions after March 13 (March 14, 2020-May 22, 2020)...10`[Cooking_Blogs_raw$...7 == "Sourdough" & is.na(Cooking_Blogs_raw$...7) == FALSE],
   Cooking_directions = Cooking_Blogs_raw$`Mentions after March 13 (March 14, 2020-May 22, 2020)...10`[Cooking_Blogs_raw$...7 == "Cooking Directions" & is.na(Cooking_Blogs_raw$...7) == FALSE],
   Cook = Cooking_Blogs_raw$`Mentions after March 13 (March 14, 2020-May 22, 2020)...10`[Cooking_Blogs_raw$...7 == "Cook" & is.na(Cooking_Blogs_raw$...7) == FALSE]))
##Twitter time 1  
cooking_data <-rbind(cooking_data, data.frame(
   Venue = "Twitter",
   Timepoint = 1,
 Recipes = Cooking_Twitter_raw$`Mentions before March 13 (January 3, 2020-March 12, 2020)...8`[Cooking_Twitter_raw$...7 == "Recipes" & is.na(Cooking_Twitter_raw$...7) == FALSE],
   Baking_Bread = Cooking_Twitter_raw$`Mentions before March 13 (January 3, 2020-March 12, 2020)...8`[Cooking_Twitter_raw$...7 == "Baking bread" & is.na(Cooking_Twitter_raw$...7) == FALSE], 
   Sourdough = Cooking_Twitter_raw$`Mentions before March 13 (January 3, 2020-March 12, 2020)...8`[Cooking_Twitter_raw$...7 == "Sourdough" & is.na(Cooking_Twitter_raw$...7) == FALSE],
   Cooking_directions = Cooking_Twitter_raw$`Mentions before March 13 (January 3, 2020-March 12, 2020)...8`[Cooking_Twitter_raw$...7 == "Cooking Directions" & is.na(Cooking_Twitter_raw$...7) == FALSE],
   Cook = Cooking_Twitter_raw$`Mentions before March 13 (January 3, 2020-March 12, 2020)...8`[Cooking_Twitter_raw$...7 == "Cook" & is.na(Cooking_Twitter_raw$...7) == FALSE]))
##Twitter time 2  
cooking_data <-rbind(cooking_data, data.frame(
   Venue = "Twitter",
   Timepoint = 2,
   Recipes = Cooking_Twitter_raw$`Mentions after March 13 (March 14, 2020-May 22, 2020)...10`[Cooking_Twitter_raw$...7 == "Recipes" & is.na(Cooking_Twitter_raw$...7) == FALSE],
   Baking_Bread = Cooking_Twitter_raw$`Mentions after March 13 (March 14, 2020-May 22, 2020)...10`[Cooking_Twitter_raw$...7 == "Baking bread" & is.na(Cooking_Twitter_raw$...7) == FALSE], 
   Sourdough = Cooking_Twitter_raw$`Mentions after March 13 (March 14, 2020-May 22, 2020)...10`[Cooking_Twitter_raw$...7 == "Sourdough" & is.na(Cooking_Twitter_raw$...7) == FALSE],
   Cooking_directions = Cooking_Twitter_raw$`Mentions after March 13 (March 14, 2020-May 22, 2020)...10`[Cooking_Twitter_raw$...7 == "Cooking Directions" & is.na(Cooking_Twitter_raw$...7) == FALSE],
   Cook = Cooking_Twitter_raw$`Mentions after March 13 (March 14, 2020-May 22, 2020)...10`[Cooking_Twitter_raw$...7 == "Cook" & is.na(Cooking_Twitter_raw$...7) == FALSE]))
##Forums time 1  
cooking_data <-rbind(cooking_data, data.frame(
   Venue = "Forums",
   Timepoint = 1,
 Recipes = Cooking_Forums_raw$`Mentions before March 13 (January 3, 2020-March 12, 2020)...8`[Cooking_Forums_raw$...7 == "Recipes" & is.na(Cooking_Forums_raw$...7) == FALSE],
   Baking_Bread = Cooking_Forums_raw$`Mentions before March 13 (January 3, 2020-March 12, 2020)...8`[Cooking_Forums_raw$...7 == "Baking bread" & is.na(Cooking_Forums_raw$...7) == FALSE], 
   Sourdough = Cooking_Forums_raw$`Mentions before March 13 (January 3, 2020-March 12, 2020)...8`[Cooking_Forums_raw$...7 == "Sourdough" & is.na(Cooking_Forums_raw$...7) == FALSE],
   Cooking_directions = Cooking_Forums_raw$`Mentions before March 13 (January 3, 2020-March 12, 2020)...8`[Cooking_Forums_raw$...7 == "Cooking Directions" & is.na(Cooking_Forums_raw$...7) == FALSE],
   Cook = Cooking_Forums_raw$`Mentions before March 13 (January 3, 2020-March 12, 2020)...8`[Cooking_Forums_raw$...7 == "Cook" & is.na(Cooking_Forums_raw$...7) == FALSE]))
##Forums time 2  
cooking_data <-rbind(cooking_data, data.frame(
   Venue = "Forums",
   Timepoint = 2,
   Recipes = Cooking_Forums_raw$`Mentions after March 13 (March 14, 2020-May 22, 2020)...10`[Cooking_Forums_raw$...7 == "Recipes" & is.na(Cooking_Forums_raw$...7) == FALSE],
   Baking_Bread = Cooking_Forums_raw$`Mentions after March 13 (March 14, 2020-May 22, 2020)...10`[Cooking_Forums_raw$...7 == "Baking bread" & is.na(Cooking_Forums_raw$...7) == FALSE], 
   Sourdough = Cooking_Forums_raw$`Mentions after March 13 (March 14, 2020-May 22, 2020)...10`[Cooking_Forums_raw$...7 == "Sourdough" & is.na(Cooking_Forums_raw$...7) == FALSE],
   Cooking_directions = Cooking_Forums_raw$`Mentions after March 13 (March 14, 2020-May 22, 2020)...10`[Cooking_Forums_raw$...7 == "Cooking Directions" & is.na(Cooking_Forums_raw$...7) == FALSE],
   Cook = Cooking_Forums_raw$`Mentions after March 13 (March 14, 2020-May 22, 2020)...10`[Cooking_Forums_raw$...7 == "Cook" & is.na(Cooking_Forums_raw$...7) == FALSE]))
```